Testing atlantisom: example bottom trawl survey index

### 2019-05-01 StandardSurveyTest.Rmd
species groups for CCA and NOBA, general boxes

if(initCCA) { #REPLACE WITH CCA GROUPS
  nontrawl <- c("Pisciv_T_Fish", "Shark_D", "Shark_P", "Reptile", "Mesopel_M_Fish")
  pelagics <- c("Planktiv_L_Fish", "Planktiv_S_Fish", "Benthopel_Fish", "Pisciv_S_Fish")
  demersals <- c("Pisciv_D_Fish", "Demersal_D_Fish","Demersal_E_Fish", "Demersal_S_Fish",
                 "Demersal_B_Fish", "Demersal_DC_Fish", "Demersal_O_Fish",  "Demersal_F_Fish",
                 "Shark_B", "SkateRay")
  selflats <- c("Pisciv_B_Fish")

}

if(initNEUS) {
  nontrawl <- c("Pisciv_T_Fish", "Shark_D", "Shark_P", "Reptile", "Mesopel_M_Fish")
  pelagics <- c("Planktiv_L_Fish", "Planktiv_S_Fish", "Benthopel_Fish", "Pisciv_S_Fish")
  demersals <- c("Pisciv_D_Fish", "Demersal_D_Fish","Demersal_E_Fish", "Demersal_S_Fish",
                 "Demersal_B_Fish", "Demersal_DC_Fish", "Demersal_O_Fish",  "Demersal_F_Fish",
                 "Shark_B", "SkateRay")
  selflats <- c("Pisciv_B_Fish")
}

if(initNOBA) { #REPLACE WITH NOBA GROUPS
  nontrawl <- c("Pisciv_T_Fish", "Shark_D", "Shark_P", "Reptile", "Mesopel_M_Fish")
  pelagics <- c("Planktiv_L_Fish", "Planktiv_S_Fish", "Benthopel_Fish", "Pisciv_S_Fish")
  demersals <- c("Pisciv_D_Fish", "Demersal_D_Fish","Demersal_E_Fish", "Demersal_S_Fish",
                 "Demersal_B_Fish", "Demersal_DC_Fish", "Demersal_O_Fish",  "Demersal_F_Fish",
                 "Shark_B", "SkateRay")
  selflats <- c("Pisciv_B_Fish")

}

@@

#   all fish (and sharks!! need dogfish in NEUS)
# could add groups "CEP" for cephalopod, "PWN" for prawn, etc
survspp <- funct.groups$Name[funct.groups$IsTurnedOn==1 &
                           funct.groups$GroupType %in% c("FISH", "SHARK")]

#   ~75% of boxes (leave off deeper boxes?)
#   cant think of a way to generalize across models, must be hard coded
#   hardcoded for NEUS 1.0 in trunk here
boxsurv <- c(1:21)

@@

# same selectivity for selflats and demersals for NEUS
# visualze selectivity curves for each group
par(mfrow=c(2,2))
par(mar=c(4,4,1,1))
plot(selnontrawl$agecl, selnontrawl$selex)
plot(selpelagics$agecl, selpelagics$selex)
plot(seldemersals$agecl, seldemersals$selex)
plot(selselflats$agecl, selselflats$selex)
par(mfrow=c(1,1))

@@

# specify cv by species groups
surv_cv_nontrawl <- data.frame(species=nontrawl, cv=rep(1.0,length(nontrawl)))
surv_cv_pelagics <- data.frame(species=pelagics, cv=rep(0.5,length(pelagics)))
surv_cv_demersals <- data.frame(species=demersals, cv=rep(0.3,length(demersals)))
surv_cv_selflats <- data.frame(species=selflats, cv=rep(0.3,length(selflats)))

@@

# ################# Below here is old from census for reference, delete ################
# # should return all model areas
# boxpars <- load_box(d.name, box.file)
# boxall <- c(0:(boxpars$nbox - 1))
# 
# # these are model specific, generalized above
# # if(initCCA) boxall <- c(0:88) 
# # if(initNEUS) boxall <- c(0:29)
# # if(initNOBA) boxall <- c(0:59) 
# 
# # should return all model output timesteps; need to generalize
# if(initCCA) timeall <- c(0:100) 
# if(initNEUS) timeall <- c(0:251)
# if(initNOBA) timeall <- c(0:560) 
#   
# # define set of species we expect surveys to sample (e.g. fish only? vertebrates?)
# # for ecosystem indicator work test all species, e.g.
# survspp <- funct.group.names 
# 
# # to keep plots simpler, currently hardcoded for vertebrate/fished invert groups
# if(initCCA) survspp <- funct.group.names[c(1:44, 59:61, 65:68)] 
# if(initNEUS) survspp <- funct.group.names[1:21]
# if(initNOBA) survspp <- funct.group.names[1:36]

>>>>

if(initCCA) { #Sarah's CCA Grouping
  nontrawl <- c("Shark_C","Yelloweye_rockfish","Benthopel_Fish","Pisciv_S_Fish",
                "Pisciv_T_Fish","Shark_D","Shark_P")
  pelagics <- c("Pisciv_V_Fish","Demersal_S_Fish","Pacific_Ocean_Perch","Mesopel_M_Fish",
                "Planktiv_L_Fish","Jack_mackerel","Planktiv_S_Fish","Pacific_sardine",
                "Anchovy","Herring","Pisciv_B_Fish")
  demersals <- c("Demersal_P_Fish","Planktiv_O_Fish","Demersal_D_Fish",
                 "Demersal_DC_Fish","Demersal_O_Fish","Darkblotched_rockfish",
                 "Demersal_F_Fish","Demersal_E_Fish","Bocaccio_rockfish",
                 "Demersal_B_Fish","Shark_R","Mesopel_N_Fish","Shark_B","Spiny_dogfish",
                 "SkateRay")
  selflats <- c("Pisciv_D_Fish", "Arrowtooth_flounder","Petrale_sole")
}

if(initNEUS) { # Sarah's NEUS Grouping
  nontrawl <- c("Pisciv_T_Fish", "Shark_D", "Shark_P", "Reptile", "Mesopel_M_Fish")
  pelagics <- c("Planktiv_L_Fish", "Planktiv_S_Fish", "Benthopel_Fish", "Pisciv_S_Fish")
  demersals <- c("Pisciv_D_Fish", "Demersal_D_Fish","Demersal_E_Fish", 
                 "Demersal_S_Fish","Demersal_B_Fish","Demersal_DC_Fish",
                 "Demersal_O_Fish","Demersal_F_Fish",
                 "Shark_B", "SkateRay")
  selflats <- c("Pisciv_B_Fish")
}

if(initNOBA) { # Sarah's NOBA Grouping
  nontrawl <- c("Sharks_other", "Pelagic_large","Mesop_fish")
  pelagics <- c("Pelagic_small","Redfish_other","Mackerel","Haddock",
                "Saithe","Redfish","Blue_whiting","Norwegian_ssh","Capelin")
  demersals <- c("Demersals_other","Demersal_large","Flatfish_other","Skates_rays",
                 "Green_halibut","North_atl_cod","Polar_cod","Snow_crab")
  selflats <- c("Long_rough_dab")
}

@@

#   all fish (and sharks!! need dogfish in NEUS)
# could add groups "CEP" for cephalopod, "PWN" for prawn, etc

# NOBA model has InvertType, changed to GroupType in file, but check Atlantis default
if(initNOBA) funct.groups <- rename(funct.groups, GroupType = InvertType)

survspp <- funct.groups$Name[funct.groups$IsTurnedOn==1 &
                           funct.groups$GroupType %in% c("FISH", "SHARK")]

#   ~75-80% of boxes (leave off deeper boxes?)
#   cant think of a way to generalize across models, must be hard coded in reality
#   hardcoded for NEUS 1.0 in trunk here: boxsurv <- c(1:21)
boxpars <- load_box(d.name, box.file)
# should return all model areas
# boxall <- c(0:(boxpars$nbox - 1))
boxsurv <- c(2:round(0.8*(boxpars$nbox - 1)))

@@

# same selectivity for selflats and demersals specified above
# visualze selectivity curves for each group
par(mfrow=c(2,2))
par(mar=c(4,4,1,1))
plot(selnontrawl$agecl, selnontrawl$selex)
plot(selpelagics$agecl, selpelagics$selex)
plot(seldemersals$agecl, seldemersals$selex)
plot(selselflats$agecl, selselflats$selex)
par(mfrow=c(1,1))

@@

#   define bottom trawl survey cv by group
cv.nt <- 1.0 # for large pelagics, reef dwellers, others not in trawlable habitat
cv.pl <- 0.5  # for pelagics
cv.dm <- 0.3  # for demersals
cv.fl <- 0.3  # for selected flatfish

# specify cv by species groups
surv_cv_nontrawl <- data.frame(species=nontrawl, cv=rep(cv.nt,length(nontrawl)))
surv_cv_pelagics <- data.frame(species=pelagics, cv=rep(cv.pl,length(pelagics)))
surv_cv_demersals <- data.frame(species=demersals, cv=rep(cv.dm,length(demersals)))
surv_cv_selflats <- data.frame(species=selflats, cv=rep(cv.fl,length(selflats)))

@@
